\begin{thebibliography}{99}

\bibitem{LaPuTie1} Alessandro Lapadula, Rosario Pugliese, Francesco
Tiezzi. \emph{``A formal account of WS-BPEL''}. Proc. 10th international
conference on Coordination Models and Languages (COORDINATION'08). Springer ``Lecture Notes in Computer Science''
5052. 2008.

\bibitem{BPEL10Spec} IBM, Bea, Microsoft. \emph{``Business Process Execution
Language for Web Services, Version 1.0''} - July 31, 2002. \\
(\href{http://download.boulder.ibm.com/ibmdl/pub/software/dw/specs/ws-bpel/ws-bpel1.pdf}{http://download.boulder.ibm.com/ibmdl/pub/software/dw/specs/ws-bpel/ws-bpel1.pdf})

\bibitem{BPEL11Spec} IBM, Bea, Microsoft, SAP, Siebel System. \emph{``Business
Process Execution Language for Web Services Version 1.1''} - May 5, 2003. \\
(\href{http://download.boulder.ibm.com/ibmdl/pub/software/dw/specs/ws-bpel/ws-bpel.pdf}{http://download.boulder.ibm.com/ibmdl/pub/software/dw/specs/ws-bpel/ws-bpel.pdf})

\bibitem{BPEL20Spec} OASIS \emph{``Web Services Business Process Execution
Language Version 2.0''} OASIS Standard - April 11, 2007. \\
(\href{http://docs.oasis-open.org/wsbpel/2.0/OS/wsbpel-v2.0-OS.html}{http://docs.oasis-open.org/wsbpel/2.0/OS/wsbpel-v2.0-OS.html})

\bibitem{OASISSite} OASIS (Organization for the Advancement of Structured
Information Standards). \\
Oasis Web Site:
\href{http://www.oasis-open.org/}{http://www.oasis-open.org/}

\bibitem{WSFL} IBM. Web Services Flow Language (WSFL). 2001.\\
(\href{http://xml.coverpages.org/wsfl.html}{http://xml.coverpages.org/wsfl.html})

\bibitem{XLANG} Microsoft. XLANG - XML Business Process Language. 2005 \\
(\href{http://xml.coverpages.org/xlang.html}{http://xml.coverpages.org/xlang.html})

\bibitem{XML} W3C Recommendation. \emph{``Extensible Markup Language (XML) 1.1
(Second Edition)''} August 16, 2006.\\
(\href{http://www.w3.org/TR/2006/REC-xml11-20060816}{http://www.w3.org/TR/2006/REC-xml11-20060816})

\bibitem{XML10} W3C Recommendation. \emph{``Extensible Markup Language (XML) 1.0
(Fifth Edition)''} November 26, 2008.\\
(\href{http://www.w3.org/TR/REC-xml/}{http://www.w3.org/TR/REC-xml/})

\bibitem{XMLSchema} W3C Recommendation. \emph{``XML Schema Part 0: Primer
Second Edition''} October 28, 2004.\\ 
(\href{http://www.w3.org/XML/Schema}{http://www.w3.org/XML/Schema})

\bibitem{WSDL} W3C, Official WSDL Web Site. \emph{``Services Description Working
Group''}. \\
(\href{http://www.w3.org/2002/ws/desc/}{http://www.w3.org/2002/ws/desc/})

\bibitem{WSDLEx} W3C Working Draft. \emph{``Web Services Description
Language (WSDL) Version 2.0 Part 2: Predefined Extensions''} August 3, 2004. \\
(\href{http://www.w3.org/TR/2004/WD-wsdl20-extensions-20040803/}{http://www.w3.org/TR/2004/WD-wsdl20-extensions-20040803/})

\bibitem{SOAP} W3C Recommendation. \emph{``SOAP Version 1.2 Part 1: Messaging
Framework (Second Edition)''} April 27, 2007. \\
(\href{http://www.w3.org/TR/2007/REC-soap12-part1-20070427/}{http://www.w3.org/TR/2007/REC-soap12-part1-20070427/})

\bibitem{HTTP} W3C Architecture Domain. \emph{``HTTP - Hypertext Transfer
Protocol''} Specifications, Drafts, Papers and Reports. 1999-2008\\
(\href{http://www.w3.org/Protocols/}{http://www.w3.org/Protocols/})

\bibitem{HTTP1} Tim Berners-Lee. \emph{``HyperText Transfer Protocol Design
Issues''} CERN Geneva, 1991. 
(\href{http://www.w3.org/Protocols/DesignIssues.html}{http://www.w3.org/Protocols/DesignIssues.html})

\bibitem{WEBSERVICES} Tim Berners-Lee. \emph{``Web Services, Program Integration
across Application and Organization boundaries''}  W3C Web Services
Workshop, 2002-2003.
(\href{http://www.w3.org/DesignIssues/WebServices.html}{http://www.w3.org/DesignIssues/WebServices.html})

\bibitem{SOC1} S. C. Cheung, Hui Lei, Michael R. Lyu. \emph{``Service Oriented
Computing and Applications ''} Springer London ISSN 1863-2386, February 22,
2007.  
(\href{http://www.springerlink.com/content/1863-2386}{http://www.springerlink.com/content/1863-2386})

\bibitem{WS-Addressing}  W3C Recommendation. \emph{``Web Services Addressing 1.0
- Core''} May 9, 2006. \\
(\href{http://www.w3.org/TR/2006/REC-ws-addr-core-20060509/}{http://www.w3.org/TR/2006/REC-ws-addr-core-20060509/})

\bibitem{Bruno} Bruno Giorgio \emph{``Linguaggi formali e compilatori''} 
UTET Università, ISBN 8877502045. 1992.

\bibitem{DragonBook} Alfred V. Aho, Ravi Sethi, Jeffrey D. Ullman
\emph{``Compilers: Principles, Techniques, and Tools. Second edition.''} ISBN
0-321-48681-1. 2006.

\bibitem{Java} Java Official Web
Site: \href{http://java.sun.com/}{http://java.sun.com/}

\bibitem{JavaCC} Java Compiler Compiler - The Java Parser
Generator. \\
Web Site: \href{https://javacc.dev.java.net/}{https://javacc.dev.java.net/}.

\bibitem{JJTree} JJTree Reference Documentation. \\
Web Site:
\href{https://javacc.dev.java.net/doc/JJTree.html}{https://javacc.dev.java.net/doc/JJTree.html}

\bibitem{JBI} Java Comunity Process. \emph{``Java Business Integration (JBI)
1.0 - Final Release''} JSR-000208 - August 17, 2005. \\
(\href{http://jcp.org/aboutJava/communityprocess/final/jsr208/index.html}{http://jcp.org/aboutJava/communityprocess/final/jsr208/index.html})

\bibitem{OPENESB} OpenEsb - Open Source JBI Enterprise Service Bus. \\
Web Site: \href{https://open-esb.dev.java.net/}{https://open-esb.dev.java.net/}

\bibitem{JavaWS} Java Web Start Documentation. Web Site: \\
\href{http://java.sun.com/javase/6/docs/technotes/guides/javaws/developersguide/contents.html}{http://java.sun.com/javase/6/docs/technotes/guides/javaws/developersguide/contents.html}.

\bibitem{NBPlatSite} NetBeans Platform. Web Site:
\href{http://platform.netbeans.org/}{http://platform.netbeans.org/}.

%\bibitem{ContxSensWikiPedia} Alan Dix, Tiziana Catarci, Benjamin Habegger,
%Yannis Ioannidis, Azrina Kamaruddin, Akrivi Katifori, Giorgos Lepouras,
%Antonella Poggi, Devina Ramduny-Ellis
%\emph{``Intelligent context-sensitive interactions on desktop and the web''}

\bibitem{GLFSite} Generic Languages Framework (GLF). Web Site: \\
\href{http://languages.netbeans.org/}{http://languages.netbeans.org/}.

\bibitem{GANGo4} Gamma Erich, Richard Helm, Ralph Johnson, John Vlissides
\emph{``Design Patterns: Elements of Reusable Object-Oriented Software''},
Addison-Wesley. ISBN 0-201-63361-2.

\bibitem{IMC} Lorenzo Bettini, Rocco De Nicola, Daniele Falassi, Michele Loreti
\emph{``Implementing a distributed mobile calculus using the IMC framework''}
ENTCS. Elsevier. 2006.\\
(\href{http://imc-fi.sourceforge.net/}{http://imc-fi.sourceforge.net/})

\bibitem{JAXWS} Java Comunity Process. \emph{``Java API for XML-Based Web
Services 2.0''} JSR-000224 - October 7, 2005.\\
(\href{http://jcp.org/aboutJava/communityprocess/pfd/jsr224/index.html}{http://jcp.org/aboutJava/communityprocess/pfd/jsr224/index.html})

\bibitem{AXIS} Apache Axis2 Web Services Engine. \\
Web Site: \href{http://ws.apache.org/axis2/}{http://ws.apache.org/axis2/}.

\bibitem{CXF} Apache CXF: An Open Source Service Framework. \\
Web Site: \href{http://cxf.apache.org/}{http://cxf.apache.org/}.

\bibitem{RichClientApp} Geertjan Wielenga, Jaroslav Tulach and Tim Boudreau
\emph{``Rich Client Programming: Plugging into the NetBeans Platform ''} 2007
Sun Press. ISBN 0132354802.

\bibitem{SVN} Subversion: An Open Source Version Control System. \\
Web Site: \href{http://subversion.tigris.org/}{http://subversion.tigris.org/}.

\bibitem{GCode} Google Code. Web
Site: \href{http://code.google.com/}{http://code.google.com/}.

\bibitem{GPLv3} GNU General Public License Version 3, June 29, 2007. \\ 
(\href{http://www.gnu.org/licenses/gpl-3.0.html}{http://www.gnu.org/licenses/gpl-3.0.html})

\end{thebibliography} 